\huge Tor's Usability for Censorship Circumvention

### 2016-04-18 pets2017-paper/pets2017-paper.tex
Note that we cut off at 40:08.

After instructions, researchers maintained minimal interactions with the participants, 
only answering logistical questions. Participants had
40 minutes to complete their worksheet. 
The participants do not know the details of their censorship environment,
only that they are actively being censored. Participants needed to configure Tor Browser to 
circumvent the simulated censorship.

>>>>

After instructions, researchers maintained minimal interactions with the participants, 
only answering logistical questions. Participants had
about 40 minutes to complete their worksheet.
(In our analysis we defined the cutoff time to be 40 minutes and 8~seconds
in order to include a participant who finished at the wire.)
The participants do not know the details of their censorship environment,
only that they are actively being censored. Participants needed to configure Tor Browser to 
circumvent the simulated censorship.
